Notes

### 2023-10-21 Notes.Rmd
notes reading Hobday 2023

>>>>

*[Hobday et al 2023 Nature](https://doi.org/10.1038/d41586-023-02730-2)*

_"Worryingly, the climate crisis could eventu- ally cause oceans to reach a permanent heat- wave state relative to historical baselines11, and some regions might no longer support certain species and ecosystems. The eco- systems that emerge might not operate and respond to warmer waters in ways that can be anticipated12."_
